Visualization of [fulle name] Fractional Integrals

### 2019-04-30 fractional/CMJ style files/article-template.tex
made good progress with paper, example section

Each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals, the shape of which is determined by their right edges, i.e. by the value 
of both $\alpha$ and $t$. The notion that $t$ alters the shape of the infinitesimals can easily be confirmed through visual inspection. The 
dashed grey curves and the solid grey-tinted curves in the right-most panel are not the same, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.

>>>>

As was the case for $R$, each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals, the shape of which is determined by their right edges, i.e. by the value 
of both $\alpha$ and $t$. The notion that $t$ and $\alpha$ alters the shape of the infinitesimals can easily be confirmed through visual inspection. In the case of $\alpha$: 
the grey-tinted solid curves depicted in each panel are not equal to one-another. Similarly, in the case of $t$: the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.

Interestingly, the effect of $\alpha$ on the shape of the infinitesimals which make up the regions depicted in Fige is larger than that of $t$. 
The curves associated with the ininitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their 
size are ignored). The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with 
one another).

The area associated with the regions depicted in Fig. are plotted in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray

it is $\alpha$  
Although $\alpha$ and $t$ alters the shape of the infinitesimals which make up the regions depicted in Fig.,
